Iterative Monomorphisation

### 2025-06-25 iterative_monomorphisation.tex
fix
more reviewers

To evaluate the usefulness of iterative monomorphisation as an alternative to native polymorphism, two competitive higher order polymorphic provers were run on the 1034 problem suite. We chose Leo-III and Zipperposition. Unfortunately we needed to exclude Vampire because of parsing issues\footnote{Vampire failed to parse a significant number of the benchmarks problems. The fix was unavailable for the higher-order branch of Vampire at the time of the evaluation.}.

@@

   We thank Sascha Böhme for fruitful discussions.
   We thank Jannis Limperg, Mark Summerfield, and three anonymous reviewers for suggesting textual improvements.

>>>>

To evaluate the usefulness of iterative monomorphisation as an alternative to native polymorphism, two competitive higher order polymorphic provers were run on the 1034 problem suite. We chose Leo-III and Zipperposition. Unfortunately we needed to exclude Vampire because of parsing issues\footnote{Vampire failed to parse a significant number of the benchmarks problems. The fix was unavailable for the higher order branch of Vampire at the time of the evaluation.}.

@@

   We thank Sascha Böhme for fruitful discussions.
   We thank Jannis Limperg, Mark Summerfield, and the anonymous reviewers for suggesting textual improvements.
